### 2023-08-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on Fig 8

\begin{figure*}[t]
%\begin{figure}
  \centering
  \subfigimg[width=0.48\linewidth]{(a)}{figures/SC_top.pdf}
  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(e)}{figures/MCp5_top.pdf}
  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
  in the thin fluid layer between vesicles and the stenosis geometry.
  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
  profiles are ploted at slices where the pressure gradient transitions
  from a value that is negative, zero, positive, zero, and negative. The
  right plots show the tangential stress with the five slices denoted by
  the marks. Note that the reversal in the pressure gradient occurs when
  the tangential stress is sufficiently large, in magnitude.}
%\end{figure}
\end{figure*}

>>>>

%\begin{figure*}[t]
\begin{figure}
  \centering
  \subfigimg[width=\columnwidth]{(a)}{figures/SC_top.pdf}
%  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
%  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
%  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/MCp5_top.pdf}
%  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
  in the thin fluid layer between the top of a vesicle and the stenosis
  geometry. The vesicles are (a): stiff single-component; (b):
  multicomponent. Similar velocity profiles between the bottom of the
  vesicle and the stenosis geometry. The profiles are ploted at slices
  where the pressure gradient transitions from a value that is negative,
  zero, positive, zero, and negative. The right plots show the
  tangential stress with the five slices denoted by the marks. Note that
  the reversal in the pressure gradient occurs when the tangential
  stress is sufficiently large.}
%  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
%  in the thin fluid layer between vesicles and the stenosis geometry.
%  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
%  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
%  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
%  profiles are ploted at slices where the pressure gradient transitions
%  from a value that is negative, zero, positive, zero, and negative. The
%  right plots show the tangential stress with the five slices denoted by
%  the marks. Note that the reversal in the pressure gradient occurs when
%  the tangential stress is sufficiently large, in magnitude.}
\end{figure}
%\end{figure*}
